When are Fuzzy Extractors Possible?

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex
put tcc rejection in crypto format

\documentclass[11pt]{article}

\def\shownotes{1}
\def\blinded{0}

\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}[theorem]{Construction}

@@

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,gassend2002silicon,tuyls2006puf,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources, it is often necessary to remove noise, in order to derive the same value in subsequent readings.

@@

A number of previous works in the precise knowledge setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

@@

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we construct families of distributions that no secure sketches and fuzzy extractors can secure, respectively~(the distributional uncertainty setting).

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then $\Pr[\rep(w', p) = \key] \geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins on $\gen$ and $\rep$, but $w'$ cannot be a function of $p$).
\item \emph{Security:} for any distribution $W_z\in\mathcal{W}_Z$, if $(\Key,P)\leftarrow\gen (W_z)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}_Z, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ (note that correctness holds for any $w'$ with probability $1-\delta$ over the coins of $\sketch$ and $\rec$, but $w'$ cannot be a function of $\sketch(w)$).
\item \emph{Security}: for any distribution $W_z\in\mathcal{W}_Z$, $\Hav(W_z|\sketch(W_z))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

@@

\begin{definition}
Let $\mathcal{M}$, $\chi$ be finite sets.
A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average case extractor} if for all pairs
of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security.  It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.  Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.  We defer proofs of statements in this section to \apref{sec:proof fuzz necessary}.
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \{W\}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
\[
\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
\]
In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.  Fuzzy min-entropy represents an upper bound on the security from a noisy source.  In the \secref{sec:related settings} computational setting there is evidence it may be possible to (nearly) achieve this upper bound.  However, in the information-theoretic setting there are many distributions with fuzzy min-entropy with no known fuzzy extractor~(or corresponding impossibility result).  We know show some properties of fuzzy min-entropy.
\begin{lemma}
\label{lem:conditional fuzz rule}
$\Hfuzz(W|P=p) \ge \Hfuzz(W) + \log \Pr[P=p]$.
\end{lemma}

@@

\section{Sufficiency of $\Hfuzz(W)$ in the Precise Knowledge Setting}
\label{sec:known distributions}
In this section, we show it is possible to build secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) given precise knowledge of a distribution $W$ whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and then turn to arbitrary distributions.

@@

Denote the largest number of points in a ball of radius $t$ in the support of $W$ as \[\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|.\]   For flat distributions, this quantity defines the fuzzy min-entropy,
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log \beta_{t}.\label{eq:fuzz for flat}
\end{align}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{2.5in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $ss = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss =( y, K))$
\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat distribution with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
\begin{corollary}
Let $n = \log |\mathcal{M}|$.  If $|R| \ge |\beta_{t}|\cdot n^{\omega(1)}$ then \consref{cons:universal hash} is correct with overwhelming probability.  That is, setting $\log |R| = \log \beta_{t} + \omega(\log n)$ suffices.
\end{corollary}

\noindent
\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell-1$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $ss=1,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =0,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\end{theorem}
\noindent
We provide a proof in \apref{sec:proof of layered hashing}.  The main idea is that providing the level information makes the distribution look nearly flat~(the probability of points differs by at most a factor of two).  We can apply similar techniques to \lemref{lem:flat hashing} to show security for each nearly flat distribution. Then, we show that providing the level information does not hurt security too much.

@@

We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z)) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.  It may be possible to improve parameters by ruling out only a worst case $W$.  In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.}

@@

\begin{proof}
We prove the stronger average case statement.
We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}_Z$ be the set of all distributions of the form 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} w_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) for arbitrary $b_i$ and $a_i\neq 0$.  The outcome $w\leftarrow W_z$ is sampled by sampling $w_1$ and computing $w$.  Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$. The algorithm $\sketch, \rec$ never see $Z$ only the outcome of $v\leftarrow V$.
Fix some $4\le t < \gamma$.
We show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance between points of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.\bnote{it would be nice to say what our counter example says about the binary space.}
\subsection{Implications for Computational Secure Sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

>>>>

\documentclass{llncs}
% \documentclass{llncs}
\def\shownotes{1}
\def\blinded{1}

%\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}      % [top=2cm, bottom=2cm, left=2cm, right=2cm]
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb, amsmath, amsfonts}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{color}
\usepackage{framed}
\usepackage{algpseudocode}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
%\newtheorem{claim}[theorem]{Claim}
%\newtheorem{problem}[theorem]{Problem}
\newtheorem{construction}[theorem]{Construction}

@@

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake}, \cite{monrose2002password,pappu2002physical,gassend2002silicon,tuyls2006puf,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources, it is often necessary to remove noise, in order to derive the same value in subsequent readings.

@@

A number of previous works in the precise knowledge setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining}, \cite{DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

@@

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In Section \ref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we construct families of distributions that no secure sketches and fuzzy extractors can secure, respectively~(the distributional uncertainty setting).

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $\key \in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(\key, p)\leftarrow \gen(w)$, then 
\[\Pr[\rep(w', p) = \key] \geq 1-\delta.\]
\item \emph{Security:} for any distribution $W_z\in\mathcal{W}_Z$, if $(\Key,P)\leftarrow\gen (W_z)$, then $\sd((\Key,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
\end{definition}

\noindent
Fuzzy extractors perform two tasks, information-reconciliation and privacy amplification.  The standard construction is \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness}) and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that minimally decreases the entropy of $w$, while mapping nearby $w'$ to $w$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}_Z, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$.  \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.  \rec takes an element $w'\in\mathcal{M}$ and $ss\in\{0,1\}^*$.  $(\sketch, \rec)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}$ if $\dis(w,w')\leq t$ then \[\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.\]
\item \emph{Security}: for any distribution $W_z\in\mathcal{W}_Z$, $\Hav(W_z|\sketch(W_z))\geq \tilde{m}$.
\end{enumerate}
\end{definition}

@@

\begin{definition}
Let $\mathcal{M}$, $\chi$ be finite sets.
A function $\ext: \mathcal{M}\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(\tilde{m}, \epsilon)$-average case extractor} if for all pairs
of random variables $X, Y$ over $\mathcal{M}, \chi$ such that
$\tilde{H}_\infty(X|Y) \ge \tilde{m}$, we have \[\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon.\]
\end{definition}

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}_Z, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}_Z, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ sample $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security.  It measures the functionality provided to the adversary by providing $\rep$~(since $p$ is public).  Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.  We defer proofs of statements in this section to \apref{sec:proof fuzz necessary}.
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \{W\}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
\[
\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
\]
In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.  Fuzzy min-entropy represents an upper bound on the security from a noisy source.  There is evidence it may be possible to (nearly) achieve this upper bound in the computational setting (see \secref{sec:related settings}).  However, in the information-theoretic setting there are many distributions with fuzzy min-entropy with no known fuzzy extractor~(or corresponding impossibility result).  We now show some properties of fuzzy min-entropy.
\begin{lemma}
\label{lem:conditional fuzz rule}
$\Hfuzz(W|P=p) \ge \Hfuzz(W) + \log \Pr[P=p]$.
\end{lemma}

@@

\section{Sufficiency of $\Hfuzz(W)$ in the Precise Knowledge Setting}
\label{sec:known distributions}
In this section, we build a secure sketch~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) for each distribution $W$ with $\Hfuzz(W) = \omega(\log n)$~(using precise knowledge of $W$).
We begin with flat distributions and then turn to arbitrary distributions.

@@

\noindent
Denote the largest number of points in a ball of radius $t$ in the support of $W$ as \[\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|.\]   For flat distributions, this quantity defines the fuzzy min-entropy,
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right| \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log \beta_{t}.\label{eq:fuzz for flat}
\end{align}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{1.8in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $ss = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss =( y, K))$
\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\begin{lemma}
\label{lem:flat hashing} (Proof in \apref{sec:proof of flat hashing})
Let $W$ be a flat with $\Hoo(W)\ge m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, \{W\}, m - \log |R|, t)$-known distribution secure sketch with error $\delta \le \frac{\beta_{t}-1}{|R|}$. 
\end{lemma}
%\noindent
%\consref{cons:universal hash} writes down enough information to disambiguate any ball of points.  The remaining entropy for this construction is $\Hav(W |\sketch(W)) = \Hoo(W) - \log \beta_{t} -\log 1/\delta$. For a flat distribution this is within a superlogarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). By choosing $\delta$ based on $\Hfuzz(W)$ we build $(\sketch, \rec)$ such that $\Hav(W | \sketch(W)) = \omega(\log n)$.

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell-1$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{2.5in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. \\
Set $ss=1,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that \\$\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =0,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, \\if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\end{theorem}
\noindent
We provide a proof in \apref{sec:proof of layered hashing}.  The main idea is that providing the level information makes the distribution look nearly flat~(the probability of points differs by at most a factor of two).  We can apply  techniques from \lemref{lem:flat hashing} to show security for each nearly flat distribution. Then, we show that providing the level information does not hurt security too much.

@@

We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary randomly samples $W_z\leftarrow \mathcal{W}_Z$ 3) the adversary wins if $\Hav(W_z|\sketch(W_z ) ) < \tilde{m}$.\footnote{Our results rule out security for an average member of $\mathcal{W}$.  It may be possible to improve parameters by ruling out only a worst case $W$.  In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.}

@@

\begin{proof}
We prove the stronger average case statement.
We first describe a family $\mathcal{W}_Z$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}_Z$ be the set of all distributions of the form 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} w_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
The family is defined by the parameters $a_2,.., a_\gamma$ and $b_2,..., b_\gamma$ (seen by the adversary) for arbitrary $b_i$ and $a_i\neq 0$.  The outcome $w\leftarrow W_z$ is sampled by sampling $w_1$ and computing $w$.  Each distribution $W_z$ is an affine line in space $\mathbb{F}^\gamma$. The algorithm $\sketch, \rec$ never see $Z$ only $ V$.
Fix some $4\le t < \gamma$.
We show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W_z\in \mathcal{W}_Z$, $\Hfuzz(W_z) = \omega (\log n)$. 
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance between points of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is a tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
\subsection{Implications for Computational Secure Sketches}
\label{sec:feas comp sec sketch}
Fuller et al.~show that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  
The definition of Fuller et al.~uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

\begin{definition}
\label{def:relaxed hill}
$W|S$ has \emph{relaxed HILL entropy},
denoted $H^{\hillrlx}_{\epsilon_{sec}, s_{sec}}(W|S)\geq \tilde{m}$, if there exists a joint distribution $(X, Y)$, such that $\tilde{H}_\infty(X|Y)\geq \tilde{m}$ and \[\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,Y))\leq \epsilon_{sec}.\]
\end{definition}

%A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ to the definition, representing the distinguishing circuit).  
\noindent
By the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:
